Vision-Based Automatic Landing of Drones

### 2024-10-20 Article/Article.tex
Continue related work and adding framework

\usepackage{amssymb,amsmath,latexsym}
\usepackage{soul,color}
\usepackage{xcolor}
\usepackage{graphicx,amssymb,amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{pgfplots}
\usepackage{array}
\usepackage[utf8]{inputenc}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\usepackage{tikz}
\usepackage{caption}
\setcounter{secnumdepth}{4}
\usepackage{pgfplots}
\usepackage{hyperref}
\usepackage{float}
\usepackage{subcaption}
\pgfplotsset{compat=newest}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{array}
\usepackage{graphicx}
%\usepackage{authblk}
\usepackage{multirow}

@@

\begin{keyword}
Visual-Based Landing; Autonomous Landing; Accurate Landing; Spoken Language Recognition.
\end{keyword}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=11.0cm]{Schematic_for_automatic_landing.png}
    \caption{Schematic for automatic landing.}
    \label{fig:Schematic_for_automatic_landing.}
\end{figure}

@@

\section{Related Work} \label{sec:related}
\subsection{Obstacle Avoidance}
Obstacle avoidance is a critical aspect of autonomous drone operations, especially in dynamic environments where both static and moving obstacles are present. One approach is integrating depth images with an occupancy voxel map to detect and track dynamic obstacles \cite{xu2023real}. This approach effectively balances computational efficiency with the need for accurate detection and tracking, making it suitable for real-time UAV operations. Another approach is.... \cite{redmon2017yolo9000}

% \cite{lee2022camera} is a set.

@@

\section{Datasets} \label{sec:datasets}

In the field of speech recognition, the ability to accurately transcribe

\section{Framework} \label{sec:framework}

>>>>

\usepackage{amssymb,amsmath,latexsym}
\usepackage{soul,color}
\usepackage{xcolor}
\usepackage{graphicx,amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{pgfplots}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\usepackage{tikz}
\usepackage{caption}
\setcounter{secnumdepth}{4}
\usepackage{hyperref}
\usepackage{float}
\usepackage{subcaption}
\pgfplotsset{compat=newest}
%\usepackage{authblk}
\usepackage{multirow}

@@

        \begin{keyword}
            Visual-Based Landing \sep Autonomous Landing \sep Accurate Landing\sep Spoken Language Recognition.
        \end{keyword}

@@

    \begin{figure}[htp]
        \centering
        \includegraphics[width=11.0cm]{Schematic_for_automatic_landing.png}
        \caption{Schematic for automatic landing.}
        \label{fig:Schematic_for_automatic_landing.}
    \end{figure}
    \\

@@

    \newpage \section{Related Work} \label{sec:related}

    \subsection{Obstacle Avoidance}
    Obstacle avoidance is a critical aspect of autonomous drone operations, especially in dynamic environments where both static and moving obstacles are present. One approach is integrating depth images with an occupancy voxel map to detect and track dynamic obstacles \cite{xu2023real}. This approach effectively balances computational efficiency with the need for accurate detection and tracking, making it suitable for real-time UAV operations. Another approach involves deep learning techniques like the YOLO (You Only Look Once) framework, which excels at real-time obstacle detection in dynamic environments \cite{redmon2017yolo9000}. YOLO9000 enables rapid detection of multiple objects, making it ideal for fast decision-making in complex surroundings. Its efficiency and accuracy have made it a popular choice for enhancing UAV obstacle avoidance systems.

    \subsection{Motion Detection and Object Detection: Yolo (You Only Look Once)}
    Recent advancements in motion and object detection have been significantly influenced by the YOLO (You Only Look Once) framework. As highlighted by \cite{dahirou2021motion}, YOLO enables real-time object detection by predicting bounding boxes and class probabilities from full images in a single evaluation, enhancing both speed and accuracy. This capability makes YOLO particularly effective for applications requiring immediate responsiveness, such as surveillance and autonomous navigation.

    \subsection{Speech Recognition}
    Speech recognition has been explored as a key component in enhancing drone operation through voice commands, particularly in environments where manual control is impractical. Various systems have been developed for continuous speech recognition on Android devices, such as the one proposed by Srivastav et al. \cite{SpeechRecognition}, which enables real-time voice command processing for mobile platforms. This technology is critical for integrating human-drone interaction, especially in hands-free scenarios, allowing operators to issue commands without physical intervention. Such advancements enable drones to act upon voice inputs for tasks like navigation, object detection, or activation of specific modes. Similar systems have been implemented to facilitate the control of unmanned aerial vehicles (UAVs) in real-time, optimizing human-machine interaction and expanding the use cases for drones in dynamic, complex environments.

    \subsection{A Robust and Accurate Landing Methodology for Drones on Moving Targets}
    Recent work has explored the use of ArUco markers for precision landing in autonomous drones, offering an efficient visual processing solution for target detection and tracking. As demonstrated in \cite{drones6040098}, ArUco markers provide high accuracy in identifying landing zones, especially when combined with robust visual algorithms. This approach addresses common challenges such as variable lighting conditions and drone stability during descent. Implementing these markers has shown success in enhancing landing precision, contributing to safer and more reliable autonomous operations.

    \subsection{An improved Canny edge detection algorithm}
    Edge detection algorithms play a critical role in enhancing the visual processing capabilities of drones by accurately identifying boundaries and objects within an image. The Canny Edge Detection Algorithm, as discussed in \cite{rong2014improved}, has proven to be highly effective due to its ability to detect edges with minimal noise while maintaining high accuracy. This method ensures that drones can detect and track obstacles, aiding in precise navigation and autonomous landing. Its application in real-time drone systems highlights its importance in improving the robustness of visual navigation and obstacle avoidance.
% \cite{lee2022camera} is a set.

@@

% \section{Datasets} \label{sec:datasets}

% In the field of speech recognition, the ability to accurately transcribe

    \section{Drone Control Mechanisms} \label{sec:framework}
    The drone’s movement is governed by four fundamental control parameters: yaw, pitch, roll, and throttle. These parameters allow the drone to maneuver in 3D space with precision, facilitating both object tracking and navigation during various flight operations.\\
    \begin{description}
        \item $\bullet$ Yaw - controls the rotation around the vertical axis, allowing the drone to turn left or right to face objects.
        \item $\bullet$ Pitch - adjusts the forward and backward tilt, moving the drone in those directions.
        \item $\bullet$ Roll - manages side-to-side tilt, shifting the drone left or right.
        \item $\bullet$ Throttle - regulates altitude by increasing or decreasing the drone’s lift.
    \end{description}
    //Maybe add more? about the remote also?

    \section{Framework} \label{sec:framework}
    \subsection{Speech Recognition}
    The speech recognition system continuously listens for voice commands, enabling real-time control of the drone without touching the screen. \\
    Each recognized command triggers a specific action in the drone. The key commands and their associated actions are:
    \begin{description}
        \item $\bullet$ Takeoff - Initiates the drone's takeoff sequence, lifting it to a designated altitude for hover.
        \item $\bullet$ Land - Initiates the landing sequence, lowering the throttle for a controlled descent until the drone reaches the ground.
        \item $\bullet$ Stop - Halts any current movement, keeping the drone stationary in hover mode.
        \item $\bullet$ Move up - Increases the throttle to elevate the drone vertically.
        \item $\bullet$ Move down - Decreases the throttle, causing the drone to descend.
        \item $\bullet$ Start recording - Begins video recording using the drone's camera.
        \item $\bullet$ Stop recording - Stops the video recording and saves the footage.
        \item $\bullet$ Edge detection - Activates the edge detection algorithm, allowing the system to identify and process edges for navigation or object tracking.

    \end{description}
    \subsection{Object Tracking?}
    \subsection{Landing Algorithm}
    \subsection{Movement Detection}
